Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-15 ms.tex
re-wrote paragraph about 545 GHz optical depth and 545 GHz monochromatic intensity estimates

We also compute the corresponding estimate of the monochromatic two-component 
intensity at 545 GHz, $M_{545}$ = $\langle M_{545, j} \rangle$ = 
$\langle \tilde{I}_{545, j}/b_{545}(T_{2,j}) \rangle$  and its variance. 
$M_{545}$ is of more general utility in making foreground predictions because 
it provides the normalization for the two-component spectrum $M_{\nu}$, 
independent of the \PLANCK~545 GHz bandpass. Lastly, we compute the 545 GHz
optical depth as $\tau_{545}$ = $\langle \tau_{545, j} \rangle$ = 
$\langle M_{545, j}/S_{545, j} \rangle$ and its variance, with the source 
function $S_{545}$ calculated according to Equation \ref{eqn:source}.

>>>>

Lastly, during post burn-in sampling, we also estimate the monochromatic 
two-component intensity at 545 GHz, $M_{545}$ = $\langle M_{545, j} \rangle$ = 
$\langle \tilde{I}_{545, j}/b_{545}(T_{2,j}) \rangle$, its variance, and
the 545 GHz optical depth $\langle \tau_{545, j} \rangle$ = 
$\langle M_{545, j}/S_{545, j} \rangle$ and its variance. $\tau_{545}$ and 
$M_{545}$ are more readily useful than the sampling parameters themselves for 
translating our fit results into predicted reddening ($\S$\ref{sec:ebv}) and 
thermal dust emission ($\S$\ref{sec:lofreq}), respectively.

%$M_{545}$ is of more general utility in making foreground predictions because 
%it provides the normalization for the two-component spectrum $M_{\nu}$, 
%independent of the \PLANCK~545 GHz bandpass. Finally, we acompute the 545 GHz
%optical depth as $\tau_{545}$ = and its variance, with the source 
%function $S_{545}$ calculated according to Equation \ref{eqn:source}.
